Eval expressions

### 2021-01-18 analysis/expressions.Rmd
Fix number of call sites evaluating only variables

There are `r nb_value_type` such call sites.

@@

```{r}
with_var <- E %>%
  filter(str_detect(expr_resolved, "^(?:\\.[:alpha]|[:alpha:])[[:alpha:][:digit:]_\\.]*$")) %>%
  filter(expr_resolved == "NA") # "NA" matches the regex of a variable name but is a value so we get rid of it
```

>>>>

There are `r nb_value_type %>% nrow()` such call sites.

@@

```{r}
with_var <- E %>%
  filter(str_detect(expr_resolved, "^(?:\\.[:alpha]|[:alpha:])[[:alpha:][:digit:]_\\.]*$")) %>%
  filter(expr_resolved != "NA") # "NA" matches the regex of a variable name but is a value so we get rid of it
```
